\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xifthen}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
  \ifthenelse{\isempty{#5}}
  {  	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  		\textbf{#1} & #2 \\
  		\textit{\small#3} & \textit{\small #4} \\
  	\end{tabular*}\vspace{-7pt}
  }
  {
  	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  		\textbf{#1} & #2 \\
  		\textit{\small#3} & \textit{\small #4} \\
  		\multicolumn{2}{p{0.97\textwidth}}{\small #5}\\
  	\end{tabular*}\vspace{-7pt}
  }
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Giorgio Caizzi} \\ 
    \vspace{1pt} 4 - 09 - 1995 $|$ Milan, Italy \\
    \small +39 340 8247713 $|$ \href{mailto:x@x.com}{\underline{giocaizzi@gmail.com}}\\ 
    \href{https://linkedin.com/in/giorgio-caizzi/}{\underline{linkedin.com/in/giorgio-caizzi/}}\\
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Environmental Engineer}{Feb.2021}
        {AECOM URS Italy S.p.a.}{Milan, Italy}
        {Technical consultancy on remediation procedures in contaminated industrial sites across Italy
          in compliance with "D.Lgs.152/06", the Italian law on environmental protection.}
        \resumeItemListStart
        \resumeItem
          {Design and implementation of remediation technogies in contaminated sites.}
        \resumeItem
          {Spatial data collection, cleaning, analysis and elaboration.}
        \resumeItem
          {Developing custom solutions for effective restitution of environmental spatial
          data.}  
        \resumeItem
          {Relations with national competent authorities.} 
  
      \resumeItemListEnd
  
      %wiseair
      \resumeSubheading
        {External Collaborator}{Mar. 2020 -- Dec. 2020}
        {Wiseair S.r.l.}{Milan, Italy}
        {Development of a GIS-based framework for spatial interpolation of PM2.5 concentration 
        data from a dense network of measuring stations, taking into account the physical 
        modifications on pollutant diffusion due to the urban morphology.}
      \resumeItemListStart
        \resumeItem
          {Automated Python processing of geographical database features.}
        \resumeItem
          {Development of tool to assess compliance with air quality international health guidelines
           in Milan, Italy.}
      \resumeItemListEnd
 
      %redbull
      \resumeSubheading
        {Event specialist - “Citycrusher” Team}{Sep. 2017 -- Sep. 2020}
        {Red Bull S.r.l.}{Milan, Italy}
        {Managining brand-activation of \textit{Red Bull Citycrusher} event-car in selected sport
         events in Italy.}

      \resumeSubheading
        {“Hero Team” Promoter}{May. 2014 -- Sep. 2019}
        {GoPro EMEA}{Munich, Germany}
        {Promotion of cameras and brand-activation in selected events in Europe.}

    % -----------Multiple Positions Heading-----------
      % \resumeSubSubheading
      %   {Software Engineer I}{Oct 2014 - Sep 2016}
      %   \resumeItemListStart
      %     \resumeItem{Apache Beam}
      %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
      %   \resumeItemListEnd
    %-------------------------------------------

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MSc in Environmental and Land Planning Engineering}{Milan, Italy}
      {Politecnico di Milano}{Sep. 2018 -- Dec. 2020}
      {\scriptsize Data structures, analysis \& ML for environment - Advanced Statistics - Advanced GIS -
       Remote Sensing - Photogrammetry -
      Sustainability \& LCA assessment - Climate change mitigation\newline
        {\scriptsize Thesis: \it “Spatial interpolation methods for producing high-resolution PM2.5 
        concentration maps in Milan, Italy“}}
    \resumeSubheading
      {BSc in Environmental and Land Planning Engineering}{Milan, Italy}
      {Politecnico di Milano}{Sep. 2014 -- Mar. 2018}
      {\scriptsize Statistics - Chemistry - Geology - Hydrology \& Hydraulics 
        - Soil \& groundwater remediation - Geotechnology - Energy engineering - GIS\newline
        {\scriptsize Thesis: \it “Estimation of the environmental and economical impact of Case dell'Acqua,
         a free drinking-water distribution project in Milan by MM S.p.a.“}}
    \resumeSubheading
     {The British School of Brussels}{Brussels, Belgium}
     {International Baccalaureate (IB Diploma)}{Sep. 2012 -- May. 2014}{}
   \resumeSubHeadingListEnd

%-----------Other SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{GIS \& CAD}{: ArcGIS \& QGis, AutoCAD, Civil3D} \textbf{Advanced Microsoft Office}{: PowerQuery \& PowerBI} \\
     \textbf{Cloud \& Automation}{: Amazon Web Services (AWS), Google Cloud Platform (GCP) \& GitHub actions}\\
     \textbf{Software Development}{: git, Unit testing \& Integration testing, Documentation, CI \& CD}\\
     \textbf{Programming}{: python, shell scripting, SQL \& PostGIS}\\
     \textbf{Python libraries}{: pytest, request, pandas, numpy, scipy, matplotlib, statsmodels, geopandas, shapely, rasterio, sphinx}\\
     \textbf{Writing}{: \LaTeX\:, Markdown \& StructuredText}     \textbf{Web}{: HTML \& CSS}\\


}}
 \end{itemize}


%-----------PERSONAL SKILLS-----------
\section{Personal skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Fluency in Italian (mothertongue) and English. French at intermediate level.} \\
     \textbf{Personal interests}{: skiing, surfing, road-cycling and outdoors. Photography.}\\
}}
 \end{itemize}

%-----------LICENSES-----------
\section{Licenses}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Italian National Assotiation of Engineers}{: Exam passed on November 2021.} \\}}
 \end{itemize}

\centering
\textbf{References and letters of recommendation available on request.}

%-------------------------------------------
\end{document}