\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------
% import from CV.sty with the necessary packages
% document definition and custom commands
\usepackage{CV}

%-----------------------------------------------
% CV starts here
\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \bfseries Giorgio Caizzi} \\
  \vspace{3pt} 4 - 09 - 1995 $|$ Milan, Italy \\
  \small +39 340 8247713 $|$ \href{mailto:giocaizzi@gmail.com}{\underline{giocaizzi@gmail.com}}\\
  \vspace{3pt}
  \faLinkedinSquare{} : \href{https://linkedin.com/in/giorgio-caizzi/}{\underline{giorgio-caizzi}}
  \faGithubSquare{} : \href{https://www.github.com/giocaizzi/}{\underline{giocaizzi}}\\
\end{center}
\vspace{-30pt}

%-----------EXPERIENCE-----------
\section{Experience}
% start list
\sectionElementListStart

% aecom
\sectionElement
{Environmental Engineer}{Feb. 2021}
{AECOM URS Italia S.p.A.}{Milan, Italy}
{
  Technical consultancy on remediation procedures in industrial sites across Italy, in compliance with D.Lgs.152/06.
}
{
  {
      Developing custom solutions for effective collection, processing, analysis and restitution of environmental data.

    },
  {
      Project management: budgeting, planning, billing and reporting. Meetings with clients.
    },
  {
      Design and implementation of investigation and remediation activities for contaminated water and soil matrices.
    },
  {
    Field supervision of technical activities carried out by subcontractors.
    },
  {
      Relations with national authorities (ARPA, Ministry of Environment) and local authorities.
    }
}


%wiseair
\sectionElement
{External Collaborator}{Mar. 2020 -- Dec. 2020}
{Wiseair S.r.l.}{Milan, Italy}
{
  Development of a GIS-based framework for spatial interpolation of PM2.5 concentration
  data, using real-time data from a dense network of measuring stations and taking into account the contribution of
  urban morphology in the dispersion of pollutants.
}
{
  {
      Automated processing of real-time pollutant concentration data, using python and GIS tools.
    },
  {
      Development of a tool to assess compliance with air quality international health guidelines.
    }
}

%redbull
\sectionElement
{Event specialist - “Citycrusher” Team}{Sep. 2017 -- Sep. 2020}
{Red Bull S.r.l.}{Milan, Italy}
{Managining brand-activation of \textit{Red Bull Citycrusher} event-car in selected sport
  events in Italy.}
{}

%gopro
\sectionElement
{Hero Team Promoter}{May. 2014 -- Sep. 2019}
{GoPro EMEA GmbH}{Munich, Germany}
{Promotion of cameras and brand-activation in selected events in Europe.}
{}
% -----------Multiple Positions Heading-----------
% \subSubHeading
%   {Software Engineer I}{Oct 2014 - Sep 2016}
%   \sectionElementSubListStart
%     \sectionElementSubListItem{Apache Beam}
%       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%   \sectionElementSubListEnd
%-------------------------------------------
\sectionElementListEnd


%-----------EDUCATION-----------
\section{Education}
\sectionElementListStart

% polimi msc
\sectionElement
{MSc in Environmental and Land Planning Engineering}{Milan, Italy}
{Politecnico di Milano}{Sep. 2018 -- Dec. 2020}
{\scriptsize Data structures, analysis \& ML for environment - Advanced Statistics - Advanced GIS -
  Remote Sensing - Photogrammetry -
  Sustainability \& LCA assessment - Climate change mitigation\newline
  {\scriptsize Thesis: \it “Spatial interpolation methods for producing high-resolution PM2.5 concentration maps in Milan, Italy“}}
{}
% polimi bsc
\sectionElement
{BSc in Environmental and Land Planning Engineering}{Milan, Italy}
{Politecnico di Milano}{Sep. 2014 -- Mar. 2018}
{\scriptsize Statistics - Chemistry - Geology - Hydrology \& Hydraulics
  - Soil \& groundwater remediation - Geotechnology - Energy engineering - GIS\newline
  {\scriptsize Thesis: \it “Environmental and economical impact of Case dell'Acqua,a free drinking-water distribution project in Milan by MM S.p.a.“}}
{}

% bsb
\sectionElement
{The British School of Brussels}{Brussels, Belgium}
{International Baccalaureate (IB Diploma)}{Sep. 2012 -- May. 2014}
{}{}

\sectionElementListEnd

%-----------Other SKILLS-----------
\section{Technical Skills}
\skillsListStart{2}
\skillsItem{Programming}{Python, JavaScript \& shell}
\skillsItem{Web frameworks}{Flask, Django \& Express}
\skillsItem{Database}{ SQL, PostGIS \& noSQL (MongoDB)}
\skillsItem{Cloud}{AWS, GCP \& Azure}
\skillsItem{Development}{git, testing, docs \& CI/CD pipelines}
\skillsItem{API}{HTTP, REST \& GraphQL}
\skillsItem{Data Science}{pandas, numpy, scikit-learn, matplotlib, seaborn, plotly, geopandas, rasterio}
\skillsItem{GIS \& CAD}{ArcGIS \& QGis, AutoCAD, Civil3D}
\skillsItem{Business Intelligence}{Power BI (M \& DAX)}
\skillsItem{Writing}{\LaTeX\:, Markdown \& reStructuredText}
\skillsItem{Web}{HTML \& CSS}
\skillsListEnd{2}


%-----------PERSONAL SKILLS-----------
\section{Personal skills}
\skillsListStart{1}
\skillsItem{Languages}{Fluency in Italian (mothertongue) and English. French at professional level.}
\skillsItem{Personal interests}{skiing, surfing, road-cycling and outdoors. Technology and AI.}
\skillsListEnd{1}

%-----------LICENSES-----------
\section{Licenses}
\skillsListStart{1}
\skillsItem{Italian National Assotiation of Engineers}{2021}
\skillsListEnd{1}

%-----------FOOTER TEXT-----------
\rfoot{
  \textbf{References and letters of recommendation available on request.}
}


%-------------------------------------------
\end{document}