\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------
% import resume.sty with necessary packages,
% document definition and custom commands
\usepackage{resume}

%-----------------------------------------------
% CV starts here
\begin{document}

%----------HEADING----------
\resumeHeader
  {Giorgio Caizzi}
  {\emailInfo{giocaizzi@gmail.com} | \locationInfo{Milan, Italy}}
  {\linkedinLink{https://linkedin.com/in/giorgio-caizzi/} \githubLink{https://www.github.com/giocaizzi/}\\}

%-----------SUMMARY-----------
\resumeSummary{Engineer who owns systems end to end — event-driven backends, observability and IaC, with AI on top. Self-taught into code at AECOM, now a hands-on tech lead shipping production systems for banks, media and retail.}

%-----------EXPERIENCE-----------
\section{Experience}
\begin{sectionElementsList}
  \experienceElement
  {Associate Manager, Products (prev. Senior Consultant)}{May 2024 -- Present}
  {Jakala S.p.A.}{Milan, Italy}
  {}
  {{Built a production RAG over 600,000 pages of internal banking regulation (PDF, Word, Excel) as lead engineer on a year-long embedded Banca Generali engagement — structure-aware chunking, hierarchical retrieval, version-aware metadata and an event-driven sync pipeline into the bank's platforms, quality-gated by a golden evaluation set. In production, rolling out across 1,600 employees.},{Built a governed tool layer that lets AI agents run SQL and geospatial operations — a GraphQL wrapper with RBAC constraining each agent call to the user's role. Non-technical users chat with their data beside a live map; productized for clients including Regione Lombardia and NielsenIQ.},{Led the engineering team that built an AI pipeline generating on-model product photography for Benetton (ComfyUI, Flux, LoRAs on Azure GPUs) at up to 90 SKUs/day with hybrid human-and-AI QA — replacing studio photoshoots for most of the brand's ecommerce imagery by autumn 2025.},{Developed the vision-language pipeline that estimates a meal's carbohydrates from a single photo for T.Conto (a consumer nutrition app live on the App Store and Google Play), using agents to retrieve ingredient reference values from a vector store of the official food-composition tables.}}
  \experienceElement
  {Environmental Engineer}{Feb. 2021 -- May 2024}
  {AECOM URS Italia S.p.A.}{Milan, Italy}
  {Remediation of contaminated industrial sites for ENI, Q8 and the US DoD.}
  {{Built Python pipelines (geopandas, GDAL, rasterio, PostGIS) that turned days of manual GIS work into hours — open-sourced on GitHub as \href{https://github.com/giocaizzi/py3dinterpolations}{\underline{py3dinterpolations}}.}}
  \experienceElement
  {Brand Activation \& Live Events}{Nov. 2013 -- Feb. 2021}
  {Red Bull, GoPro EMEA}{Italy \& Europe}
  {Seven years of live brand-activation at major sporting events across Europe, alongside my studies — public speaking and running games/giveaways for crowds, trilingually.}
  {}
\end{sectionElementsList}

%-----------EDUCATION-----------
\section{Education}
\begin{sectionElementsList}
  \educationElementWithDetails
    {MSc (102/110) and BSc (97/110) in Environmental \& Land Planning Engineering}{Milan, Italy}
    {Politecnico di Milano}{Sep. 2014 -- Dec. 2020}
    {\degreeDetail{Relevant coursework}{computer science (30/30), GIS \& spatial data, statistical models \& stochastic processes, remote sensing}{}}
    {\degreeDetail{Theses}{PM2.5 spatial-interpolation algorithm (Wiseair S.r.l.); facility-location optimization for Milan's public water network (MM S.p.A.)}{}}
  \experienceElement
    {The British School of Brussels}{Brussels, Belgium}
    {International Baccalaureate Diploma}{Sep. 2012 -- May 2014}
    {}{}
\end{sectionElementsList}

%-----------LICENSES-----------

%-----------TECH SKILLS-----------
\section{Technical Skills}
\begin{sectionElementsList}
  \skillsElement{1}{
    \skillsItem{GenAI \& LLMOps}{RAG \& retrieval engineering, LLMs \& multimodal, agentic orchestration \& MCP, evaluation \& guardrailing, AI observability, OpenAI, Anthropic \& Azure OpenAI}
    \skillsItem{Backend \& Systems}{Python \& TypeScript, FastAPI, REST \& GraphQL, event-driven pipelines \& queues, OpenTelemetry distributed tracing, Docker, CI/CD, git}
    \skillsItem{Data}{SQL \& NoSQL, Redis, vector \& graph stores}
    \skillsItem{Cloud \& Infrastructure}{Azure, GCP, Terraform (IaC), networking, serverless}
    \skillsItem{Geospatial}{PostGIS, GDAL, geopandas, shapely, rasterio, ArcGIS \& QGIS}
  }
\end{sectionElementsList}

%-----------PROJECTS-----------
\section{Projects}
\begin{sectionElementsList}
  \projectElement{
    \href{https://github.com/giocaizzi/ralph-copilot}{ralph-copilot}
    }{
    autonomous agent loop for GitHub Copilot  \faStar 138
  }{Copilot custom agents, git-as-memory}
  \projectElement{
    \href{https://github.com/giocaizzi/greenhouse}{greenhouse}
    }{
    smart-irrigation app exposing an MCP server to LLM agents
  }{Python, FastAPI, MCP, Docker}
  \projectElement{
    \href{https://github.com/giocaizzi/btc-cycles}{btc-cycles}
    }{
    bitcoin-cycle analytics with a live daily dashboard
  }{Python, PyPI, CI/CD, plotly}
\end{sectionElementsList}

%-----------PERSONAL SKILLS-----------
\section{Personal skills}
\begin{sectionElementsList}
  \skillsElement{1}{
    \skillsItem{Languages}{Italian (native), English (bilingual), French (professional working proficiency).}
    \skillsItem{Interests}{Surfing, skiing and road-cycling, chased worldwide: Indonesia, Angola, South Africa, across Europe.}
  }
\end{sectionElementsList}

%-----------FOOTER TEXT-----------

%-------------------------------------------
\end{document}